\begin{abstract}
%
Although Bloom Filters (BF) have been widely used in many networking applications and beyond, the fundamental issue of how to calculate the false positive probability remains elusive.
%
Properly calculating the false positive probability of BF is critical because it is used to calculate the optimal number of hash functions $k$.
%
Since Bloom gave the false positive formula in 1970, in 2008, Bose \textit{et al.} pointed out that Bloom's formula for calculating the false positive probability is flawed and gave a new false positive formula; and in 2010, Christensen \etal further pointed out that Bose's formula is also flawed and gave another new false positive formula.
%
Although Christensen's formula is perfectly accurate, it is time-consuming to calculate the false positive probability, and it is impossible to calculate the derivation of the optimal value of $k$.
%
While the conventional wisdom is to derive the optimal value of $k$ from a false positive formula, in this paper, we propose the first approach to calculating the optimal $k$ without any false positive formula.
%
Our approach is based on the following observation: for a BF with $m$ bits and $n$ elements, if and only if its entropy is the largest, its false positive probability is the smallest, according to information entropy theory.
%
Furthermore, we propose a new and more accurate upper bound for the false positive probability.
%
When the size of a Bloom filter becomes infinitely large, our upper bound turns equal to the lower bound, which becomes Bloom's formula.
%
This deepens our understanding of Bloom's formula: it is perfectly accurate when $m$ is infinitely large, and it is practically accurate when $m$ is sufficiently large.
%
Besides, we derive the bounds of correct rate of counting Bloom filters (one widely used variant of BFs for estimating item frequencies) by applying our proposed formulas about BFs to them. 
% 
We release our source code of Bloom Filters in \cite{opensource} without any identity information.
\end{abstract}

%\vspace{0.15in}
%\begin{IEEEkeywords}
%Bloom Filter, False Positive Probability, Information Entropy
%\end{IEEEkeywords} 